Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2017-10-24 paper/submitted/round3_png/reviewer_response_round3.tex

We thank the reviewers for their detailed and insightful comments and helping us strengthen the manuscript. Our point-by-point responses to the critique are outlined below, with reviewer comments in black and \blue{responses in blue}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Reviewer 2}

I had three major concerns with the previous version.

My first and last concern have been dealt with.

However, my second concern (on the degree of compatibility) is not dealt with adequately (in particular, Proposition 1 is not true in general). I therefore recommend that the authors re-submit an updated version for a subsequent review. My concern is further outlined below.

Although the part below Eqs (4a) and (4b) contains some explanation regarding compatibility of $U_{HF}$ and $U_{LF}$, this is not made mathematically explicit.
Therefore the result (7) of Proposition 1 is not necessarily true. For example, there is no reason why a low-fidelity solution can be substituted in a high-fidelity (bi)linear form, as done in (7). This requires suitable compatibility of the low-fidelity space with the high-fidelity space that has not been made mathematically explicit (some inclusion is actually assumed). In the proof, for example, eq. (9) is not necessarily true.
I have two recommendations: 1. restrict the assumption of different spaces to it being the same space, or 2. introduce suitable required inclusions for these spaces.

\answer{We added a formal definition of compatibility just before Proposition 1.}

### 2017-10-27 paper/submitted/round3_png/reviewer_response_round3.tex

My first and last concern have been dealt with.

However, my second concern (on the degree of compatibility) is not dealt with adequately (in particular, Proposition 1 is not true in general). I therefore recommend that the authors re-submit an updated version for a subsequent review. My concern is further outlined below.

Although the part below Eqs (4a) and (4b) contains some explanation regarding compatibility of $U_{HF}$ and $U_{LF}$, this is not made mathematically explicit.
Therefore the result (7) of Proposition 1 is not necessarily true. For example, there is no reason why a low-fidelity solution can be substituted in a high-fidelity (bi)linear form, as done in (7). This requires suitable compatibility of the low-fidelity space with the high-fidelity space that has not been made mathematically explicit (some inclusion is actually assumed). In the proof, for example, eq. (9) is not necessarily true.
I have two recommendations: 1. restrict the assumption of different spaces to it being the same space, or 2. introduce suitable required inclusions for these spaces.

\answer{We added a formal definition explicitly describing suitable inclusions for compatibility ($U_{LF}\subseteq U_{HF}$ and $Q_{LF}\subseteq Q_{HF}$) just before Proposition 1; this allows the substitution of a low-fidelity solution into a high-fidelity form. References to this definition were added to Section 2.1 (page 7) where compatibility is first mentioned, to Proposition 1 where the assumption of compatibility is first used in proving the result in Equation 7, and to Section 3.1 (page 15-16) where we give examples of potential pairs of compatible models.}

### 2017-10-27 paper/submitted/round3_png/numerical_experiments_v6_cmame.tex
made changes based on karen's feedback

\Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. 
%
\begin{figure}[htbp]
%\captionsetup[subfloat]{captionskip=-5pt}
\centering
\subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_LF.pdf} %0.49 round1 png
  \label{fig:baseRef0}
} \\
\subfloat[MF$_1$ ($5\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF01.pdf} %0.49 round1 png
} \\
\subfloat[MF$_2$ ($10\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF02.pdf} %0.49 round1 png
} \\
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion). Right: local error contributions. }
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

@@

\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. 
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_0$ ($0\%$ HF)]{
	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_LF_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_LF.pdf} %0.49 round1 png
} \\
\subfloat[MF$_1$ ($10\%$ HF)]{
	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF01_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF01.pdf} %0.49 round1 png
} \\
\subfloat[MF$_2$ ($20\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF02_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF02.pdf} %0.49 round1 png
} \\
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_3$ ($30\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_4$ ($40\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_5$ ($50\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
\subfloat[MF$_6$ ($60\%$ HF)]{
	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF06_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF06.pdf} %0.49 round1 png
}
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion). Right: local error contributions. The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
\label{fig:svfRef}
\end{figure}
%
Comparing to \Cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest observation location; here, all three observation locations and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration. This reflects the global nature of the differences between the low- and high-fidelity models.

>>>>

\Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. 
%
\begin{figure}[htbp]
%\captionsetup[subfloat]{captionskip=-5pt}
\centering
\subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_LF.png} %0.49 round1 png
  \label{fig:baseRef0}
} \\
\subfloat[MF$_1$ ($5\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF01.png} %0.49 round1 png
} \\
\subfloat[MF$_2$ ($10\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf} %0.46 round1 png
  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF02.png} %0.49 round1 png
} \\
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion). Right: local error contributions. }
\label{fig:baseRef}
\end{figure}
%
Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.

@@

\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. 
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_0$ ($0\%$ HF)]{
	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_LF_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_LF.png} %0.49 round1 png
} \\
\subfloat[MF$_1$ ($10\%$ HF)]{
	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF01_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF01.png} %0.49 round1 png
} \\
\subfloat[MF$_2$ ($20\%$ HF)]{
  \includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF02_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF02.png} %0.49 round1 png
} \\
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_3$ ($30\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_4$ ($40\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_5$ ($50\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
\subfloat[MF$_6$ ($60\%$ HF)]{
	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF06_divvy.pdf} %0.465 round1 png
  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF06.png} %0.49 round1 png
}
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion). Right: local error contributions. The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
\label{fig:svfRef}
\end{figure}
%
Comparing to \Cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest observation location; here, all three observation locations and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration. This reflects the global nature of the differences between the low- and high-fidelity models.
